### 2016-10-04 ms/ms.tex
made pailo's comments

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was
different from what is expected by preferential attachment. Based on a
preferential attachment process, we expect that the most persistent
and high degree species would remain stable in the network core during
assembly \citep{barabasi1999emergence}. Surprisingly, however, we
encountered the opposite pattern. For example, the four most
ubiquitous species in our study landscape --- \textit{Halictus
  ligatus}, \textit{Halictus tripartitus}, \textit{Lasioglossum
  (Dialictus) incompletum}, and \textit{Toxomerus marginatus} --- were
the only species that changed which module they were a member across
years in all the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentangle
the causal mechanism for why species with those characteristics are so
variable in their network position. Generalized species may be able to
better exploit the limited floral resources in the intensively managed
agriculture landscape, and thus also be the most persistent
\flagged{any citations? I can only find articles discussing
  generalization in plants}. More persistent species usually have
longer phenologies, so they can visit many different flowers,
resulting in a higher degree \citep{Vazquez2009}. Either way, our
result suggests that adaptable species can change their network
position to utilize the most advantageous floral resources available,
which may depend on the other pollinator species that are present, and
the state of the plant community \citep{macleod2016measuring,
  gomez2006ecological, waser1996generalization}. Thus given the
opportunity and ability to use different resources, species will often
change their network positions \citep{macleod2016measuring}.

>>>>

In addition to finding multiple network organization changing points
during assembly, the way in which these reorganizations occur was
different from what is expected by preferential attachment. Based on a
preferential attachment process, we expect that the most persistent
and high degree species would remain stable in the network core during
assembly \citep{barabasi1999emergence}. Surprisingly, however, we
encountered the opposite pattern. For example, the four most
ubiquitous species in our study landscape --- \textit{Halictus
  ligatus}, \textit{Halictus tripartitus}, \textit{Lasioglossum
  (Dialictus) incompletum}, and \textit{Toxomerus marginatus} --- were
the only species that changed which module they were a member across
years in all the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentangle
the causal mechanism for why species with those characteristics are so
variable in their network position. Generalized species may be able to
better exploit the limited floral resources in the intensively managed
agriculture landscape, and thus also be the most persistent \citep[in
ant-plant mutualisms, ][]{diaz2010changes}. More persistent species
usually have longer phenologies, so they can visit many different
flowers, resulting in a higher degree \citep{Vazquez2009}. Either way,
our result suggests that adaptable species can change their network
position to utilize the most advantageous floral resources available,
which may depend on the other pollinator species that are present, and
the state of the plant community \citep{macleod2016measuring,
  gomez2006ecological, waser1996generalization}. Thus given the
opportunity and ability to use different resources, species will often
change their network positions \citep{macleod2016measuring}.
